MSDS Case Study 2 - Procrastination and HDI Data

### 2017-12-02 MSDS_CaseStudy2_Master.Rmd
Added procrastination.csv, remaining_countries.csv, and will commit again because forgot underscores

```{r Question3 HDI table scrape from Wikipedia}

@@

```{r Question4 Preliminary Analysis, warning=FALSE}

@@

h3 = gghistogram(resp_full,x='HDI',y='..count..',
								 bins=35,
								 fill='cadetblue3',
								 size=2,
								 title='Histogram of HDI',
								 color='white',
								 ylab='Count'
)

@@

#For the codebook only
#These are the job assignments we subjectively made to get the top10 job counts shown:
top_jobs = match_list(resp_full$Current_Occ,findtext=keywords$title)

for (i in 1:length(top10Jobs$title)) {
print(paste(tolower(as.character(top10Jobs$title[i])),'<-', unique(unique(top_jobs[[i]][,2]))))
}

@@

countryCt = as.data.frame(table(resp_full$Country_Res))
colnames(countryCt) = c('Country','Count')
sortedCC = countryCt[order(countryCt$Count, decreasing = TRUE),]
kable(head(sortedCC,20),row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:20,bold=T,color='white',background='darkred')
# 4E:

@@

```{r Question5 Preliminary Analysis}

@@

##Set chunk size for output
ggplot(Top15DP, aes(reorder(Country_Res, -DP_Avg), DP_Avg))+
	geom_bar(aes(fill=HDI_Cat), stat="identity")+
	ggtitle("Countries with the top 15 DPMean") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Country Name")+
	ylab("DP Mean Value")

@@

##Set chunk size for output
ggplot(Top15AIP, aes(reorder(Country_Res, -AIP_Avg), AIP_Avg))+
	geom_bar(aes(fill=HDI_Cat), stat="identity")+
	ggtitle("Countries with the top 15 AIPMean") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Country Name")+
	ylab("AIP Mean Value")

@@

par(mar=c(4,6,2,2))
plot(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = ifelse(mDFMFAvg$Gender == "Female", "hot pink", "blue"), xlab="", ylab="")
axis(1,at=pretty(mDFMFAvg$Age),labels=pretty(mDFMFAvg$Age),las=1)
axis(2,at=pretty(mDFMFAvg$Annual_Inc),labels=format(pretty(mDFMFAvg$Annual_Inc),big.mark=",", scientific=FALSE),las=1)
mtext(text="Age", side=1, line=2)
mtext(text="Annual Income", side=2, line=5)
title("Mean Income by Age and Gender")
abline(lm(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age), col = "green")

@@

par(mar=c(4,6,2,2))
plot(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = "blue", xlab="", ylab="")
axis(1,at=pretty(mDFHDIAvg$HDI),labels=pretty(mDFHDIAvg$HDI),las=1)
axis(2,at=pretty(mDFHDIAvg$SWLS_Avg),labels=format(pretty(mDFHDIAvg$SWLS_Avg),big.mark=",", scientific=FALSE),las=1)
mtext(text="HDI", side=1, line=2)
mtext(text="Mean Life Satisfaction", side=2, line=5)
title("Life Satisfaction Mean by HDI")
abline(lm(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI), col = "green")

@@

ggplot(mDFHDIAvg, aes(fill=HDI_Cat, y=SWLS_Avg, x=HDI_Cat)) + 
	scale_x_discrete(labels=c("High Human Development" = "HHD", "Very High Human Development" = "VHHD",
														"Medium Human Development" = "MHD", "Low Human Development" = "LHD")) +
	geom_bar(position="dodge", stat="identity") +
	ggtitle("Mean Life Satisfaction per HDI Category Test") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Human Development Category") +
	ylab("Life Satisfaction Mean")

>>>>

```{r Question3_HDI_table_scrape_from_Wikipedia}

@@

```{r Question4_Preliminary_Analysis, warning=FALSE}

@@

h3 = gghistogram(resp_full,x='HDI',y='..count..',
								 bins=10,
								 fill='cadetblue3',
								 size=2,
								 title='Histogram of HDI',
								 color='white',
								 ylab='Count'
)

@@

#For the codebook only
#These are the job assignments we subjectively made to get the top10 job counts shown:
top_jobs = match_list(resp_full$Current_Occ,findtext=keywords$title)
joblist_replace = character()
for (i in 1:length(top10Jobs$title)) {
joblist_replace = c(joblist_replace,paste(tolower(as.character(top10Jobs$title[i])),'<-', unique(unique(top_jobs[[i]][,2]))))
}
write.csv(joblist_replace,'Job_Keyword_Mapping.csv')

@@

countryCt = as.data.frame(table(resp_full$Country_Res))
colnames(countryCt) = c('Country','Count')
sortedCC = countryCt[order(countryCt$Count, decreasing = TRUE),]
kable(head(sortedCC,19),row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:19,bold=T,color='white',background='darkred')

write.csv(sortedCC[21:length(sortedCC$Country),],'Remaining_Countries.csv')

# 4E:

@@

```{r Question5_Preliminary_Analysis}

@@

##Set chunk size for output
ggplot(Top15DP, aes(reorder(Country_Res, -DP_Avg), DP_Avg))+
	geom_bar(aes(fill=HDI_Cat), stat="identity")+
	ggtitle("Countries with the top 15 DPMean") +
	theme(plot.title = element_text(hjust = 0.5),axis.text.x=element_text(angle=45,hjust=1)) +
	xlab("Country Name")+
	ylab("DP Mean Value")

@@

##Set chunk size for output
ggplot(Top15AIP, aes(reorder(Country_Res, -AIP_Avg), AIP_Avg))+
	geom_bar(aes(fill=HDI_Cat), stat="identity")+
	ggtitle("Countries with the top 15 AIPMean") +
	theme(plot.title = element_text(hjust = 0.5),axis.text.x=element_text(angle=45,hjust=1)) +
	xlab("Country Name")+
	ylab("AIP Mean Value")+
  scale_x_discrete(labels=c("Dominican Republic"="Dom. Republic"))

@@

#par(mar=c(4,6,2,2))
# par(xpd = T, mar = par()$mar + c(0,0,0,7))
# plot(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = ifelse(mDFMFAvg$Gender == "Female", "hot pink", "blue"), xlab="", ylab="")
# axis(1,at=pretty(mDFMFAvg$Age),labels=pretty(mDFMFAvg$Age),las=1)
# axis(2,at=pretty(mDFMFAvg$Annual_Inc),labels=format(pretty(mDFMFAvg$Annual_Inc),big.mark=",", scientific=FALSE),las=1)
# mtext(text="Age", side=1, line=2)
# mtext(text="Annual Income", side=2, line=5)
# title("Mean Income by Age and Gender")
# abline(lm(mDFMFAvg$Annual_Inc ~ mDFMFAvg$Age), col = "green")
# legend("topright",title="Gender",c("Male","Female"),fill=terrain.colors(3),horiz=TRUE)
# par(mar=c(5, 4, 4, 2) + 0.1)

h5 = ggscatter(mDFMFAvg,y='Annual_Inc',x='Age',
								 color='Gender',
								 size=2,
								 title='Average Annual Income vs Average Age',
								 ylab='Average Annual Income',
								 xlab='Average Age')

h5 = h5 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5)) +
  scale_y_continuous(label=dollar_format(),breaks = round(seq(0, max(mDFMFAvg$Annual_Inc), by = 25000),1))

h5

@@

par(mar=c(4,6,2,2))
plot(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI, xaxt="n", yaxt="n", pch = 16, cex = 1.3, col = "blue", xlab="", ylab="")
axis(1,at=pretty(mDFHDIAvg$HDI),labels=pretty(mDFHDIAvg$HDI),las=1)
axis(2,at=pretty(mDFHDIAvg$SWLS_Avg),labels=format(pretty(mDFHDIAvg$SWLS_Avg),big.mark=",", scientific=FALSE),las=1)
mtext(text="Mean HDI", side=1, line=2)
mtext(text="Mean Life Satisfaction", side=2, line=5)
title("Life Satisfaction Mean by Mean HDI")
abline(lm(mDFHDIAvg$SWLS_Avg ~ mDFHDIAvg$HDI), col = "green")

@@

mDFHDIAvg$HDI_Cat_Relevel = factor(mDFHDIAvg$HDI_Cat,levels=c('Very High','High','Medium','Low'))

ggplot(mDFHDIAvg, aes(fill=HDI_Cat_Relevel, y=SWLS_Avg, x=HDI_Cat_Relevel)) + 
	scale_x_discrete(labels=c("High Human Development" = "HHD", "Very High Human Development" = "VHHD",
														"Medium Human Development" = "MHD", "Low Human Development" = "LHD")) +
	geom_bar(position="dodge", stat="identity", width=.5) +
	ggtitle("Mean Life Satisfaction per HDI Category Test") +
	theme(plot.title = element_text(hjust = 0.5)) +
	xlab("Human Development Category") +
	ylab("Mean Life Satisfaction")
